Self Regulation Ontology Retest Analyses

### 2018-06-04 code/SRO_Retest_Analyses.Rmd
updates

Are the residuals of this model heteroscedasticity

@@

@@

lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

@@

  mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size)+task, data=sampled_df)
  mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size)+task, data=sampled_df)

@@

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("white", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(axis.title.x  = element_text(size=16),
        axis.text.x  = element_text(size=14),
        axis.title.y  = element_text(size=16),
        legend.title  = element_text(size=16),
        legend.text  = element_text(size=16))

ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)

@@

```{r}
with(comp_lit_pred_out, t.test(m_lit, m_boot))
```

@@

>>>>

Are the residuals of this model heteroscedastic? Yes the residuals do not depend on the predictor.

@@

Highlighting the difference between survey and task reliability for comparability to our results.

@@

#lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

#write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

lit_emp_cor_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

@@

  if(length(unique(sampled_df$task))>1){
    mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size)+task, data=sampled_df)
    mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size)+task, data=sampled_df)
  }
  else{
    mod_lit = lm(retest_reliability ~ lit_predictor+scale(sample_size), data=sampled_df)
    mod_boot = lm(retest_reliability ~ mean_pearson+scale(sample_size), data=sampled_df)
  }

@@

@@

@@

Are you at noise ceiling for suveys vs. tasks?

```{r}
comp_lit_pred_out_task = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="task")))
comp_lit_pred_out_task$task = "task"
comp_lit_pred_out_survey = plyr::rdply(1000, comp_lit_pred(rel_comp %>% filter(task=="survey")))
comp_lit_pred_out_survey$task = "survey"
comp_lit_pred_out_both = rbind(comp_lit_pred_out_task, comp_lit_pred_out_task)

What does it look like if you estimate the left one out using the remaining ones for the noise ceiling model?

```{r}

Literature vs. our data on a  measure basis

```{r}

Are you better in estimating the literature using our data for surveys vs tasks?

```{r}
